---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# gitignore

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/gitignore)](https://cran.r-project.org/package=gitignore)
[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/PMassicotte/gitignore?branch=master&svg=true)](https://ci.appveyor.com/project/PMassicotte/gitignore)
[![Travis build status](https://travis-ci.org/PMassicotte/gitignore.svg?branch=master)](https://travis-ci.org/PMassicotte/gitignore)
[![Codecov test coverage](https://codecov.io/gh/PMassicotte/gitignore/branch/master/graph/badge.svg)](https://codecov.io/gh/PMassicotte/gitignore?branch=master)
<!-- badges: end -->

The package `gitignore` provides a simple R interface to the [gitignore.io](https://gitignore.io/) API. It can be used to fetch gitignore templates that can be included into the `.gitignore` file of you git repository.

## Installation

You can install the released version of gitignore from [CRAN](https://CRAN.R-project.org) with:

```{r, eval=FALSE}
install.packages("gitignore") # Not currently published on CRAN
```

Or the dev version with: 

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("pmassicotte/gitignore")
```

## Examples

There are currently two useful functions in the package:

- `gi_available_templates()` to fetch all supported gitignore templates.
- `gi_fetch_templates()` to fetch one or many gitignore templates.

```{r}
library(gitignore)

head(gi_available_templates(), 25)
```

Templates can be fecthed using the `gi_fetch_templates()` function.

```{r, results='markup', comment=""}
gi_fetch_templates("R")
```

Multiple templates can be fetched by specifying multiple values:

```{r, results='markup', comment=""}
gi_fetch_templates(c("java", "c++"))
```

## Code of conduct

Please note that the 'gitignore' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
