---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Basic idea

Based on the definition proposed by [freecodecamp](https://guide.freecodecamp.org/git/gitignore/):

> The .gitignore file is a text file that tells Git which files or folders to ignore in a project. A local .gitignore file is usually placed in the root directory of a project. You can also create a global .gitignore file and any entries in that file will be ignored in all of your Git repositories.

For any project, it is therefore important to have a `.gitignore` file that is complete and accurate. The package `gitignore` provides a simple R interface to the [gitignore.io](https://gitignore.io/) API. It can be used to fetch gitignore templates that can be included into the `.gitignore` file of you git repository. The `gitignore` R package can be used with R package, R Studio project or with any `.gitignore` file. Note that be default, the `usethis` package populates the `.gitignore` for the R language when you create a R project. However, it is common to use many different programming languages in a project such as `LaTeX`, `python`, `matlab`, `julia` and so one. This is where the `gitignore` package shines as it can be used to programmatically modify the `.gitignore` file of your project.

`gitignore` is a simple R package that provide an interface to query [gitignore.io](https://gitignore.io/) to fetch gitignore templates that can be included in the .gitignore file. More than 450 templates are currently available. There are actually two functions in the package:

- `gi_available_templates()`: to get a list of all templates available on [gitignore.io](https://gitignore.io/).
- `gi_fetch_templates()`: to get one or more template(s). This function can copy the returned template(s) in the clipboard as well as happening the the `.gitignore` file in your project directory.

## Examples

```{r setup}
library(gitignore)
```

Get the list of all available templates from [gitignore.io](https://gitignore.io/):

```{r}
head(gi_available_templates(), 50)
```

The function `gi_fetch_templates()` can be used to fetch particular template(s). For example, one could want to get the `java` and `c++` templates as follow:

```{r}
gi_fetch_templates(c("java", "c++"))
```

By default, the template(s) are not copied into the clipboard, this can be changed by setting `copy_to_clipboard = TRUE`:

```{r, eval=FALSE}
gi_fetch_templates(c("java", "c++"), copy_to_clipboard = TRUE)
```

Additionally, you can tell `gi_fetch_templates()` to append automatically the `.gitignore` file in your project by setting `append_gitignore = TRUE`:

```{r, eval=FALSE}
gi_fetch_templates(c("R"), append_gitignore = TRUE)
```

It is also possible to specify the `.gitignore` file to be modified by specifying the `gitignore_file` argument.

```{r, message=TRUE}
f <- paste0(tempdir(), "/.gitignore")

file.create(f)

gi_fetch_templates("R", gitignore_file = f, append_gitignore = TRUE)
  
readLines(f)
  
```

