---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Basic idea

`gitignore` is a simple R package that provide an interface to query [gitignore.io](gitignore.io) to fetch gitignore templates that can be included in the .gitignore file. More than 450 templates are currently available. There are actually two functions in the package:

- `gi_available_templates()`: to get a list of all templates available on [gitignore.io](gitignore.io).
- `gi_fetch_templates()`: to get one or more template(s). This function can copy the returned template(s) in the clipboard as well as happening the the `.gitignore` file in your project directory.

## Examples

```{r setup}
library(gitignore)
```

Get the list of all available templates from [gitignore.io](gitignore.io):

```{r}
head(gi_available_templates(), 50)
```

The function `gi_fetch_templates()` can be used to fetch particular template(s). For example, one could want to get the `java` and `c++` templates as follow:

```{r}
gi_fetch_templates(c("java", "c++"))
```

By default, the template(s) are copied into the clipboard, this can be changed by setting `copy_to_clipboard = FALSE`:

```{r}
gi_fetch_templates(c("java", "c++"), copy_to_clipboard = FALSE)
```

Additionally, you can tell `gi_fetch_templates()` to append automatically the `.gitignore` file in your project by setting `append_gitignore = TRUE`:

```{r, eval=FALSE}
gi_fetch_templates(c("java", "c++"), append_gitignore = TRUE)
```
